\section*{Outlines}
\begin{itemize}
    {\item \textbf{Literature Review} {\footnotesize(partially done)}}

    Searching the literature to get a better and clearer understanding of the theoretical 
    and the applied aspects of the topic. This will also help us to determine a relevant industrial problem.

    {\item \textbf{Establishing Connection with Industry}
    {\footnotesize(in progress)}}

    We are currently trying to contact potential companies and organization in order get an industrial 
    support and insight for the project. We are also, trying to find suitable industrial advisor 
    that has an experience in the related field.

    {\item \textbf{Reproducing Previous work} {\footnotesize(partially done)}}

    In order to deepen our understanding of the topic and have more confidence in our work and implementation, 
    we are trying to produce some the previous work in the literature.

    {\item \textbf{Solving the Main problem }}
    
    At this stage, we should be able to apply the skills and the methods that 
    we have searched about and developed to solve the industrial problem.

     {\item \textbf{Validating the Results }}

     After solving the problem, we need to validate our results by analyzing the obtained data.

    {\item \textbf{Demonstration}} 

    Preparing a demonstration to advertise or show the applicability of the project to solve actual problems. 
    This also includes preparing a poster, a report, and a presentation.

    {\item \textbf{Submitting the Project}} 
    
    At this stage, we should make a final review and corrections if necessary before the final submission. 
\end{itemize}